Viscous Transport in Eroding Porous Media

### 2019-05-24 docs/transport/erosion_transport.tex
do the result section in transport paper

We also do not use any fast summation methods to apply the Barycentric
quadrature rule.  Since this quadrature rule is applied at every GMRES
iteration, it is imperative that we only apply the Barycentric
quadrature at target points where they are required.  As a rule of
thumb, the trapezoid rule due to $\gamma_k$ is accurate if
\begin{align}
  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| < 
    5 \frac{L_k}{N_\iin}.
\end{align}
To avoid having to check if a target point $\xx$ satisifies

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We do some simulations.  The parameters are
\begin{itemize}
  \item time step size
  \item regularization and smoothing parameters
  \item resolution on bodies and solid wall
\end{itemize}
{\color{red} In this section, we present the numerical simulations of bodies eroding in the fluid. The computational domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded off corners and we place bodies only in $[-1,1]\times[-1,1]$. We impose the fixed-pressure-drop condition on the simulation
 smoothing parameters of $\eps$ and $\sigma $.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A single body close to a wall}
\todo[inline]{Do a single body that is extremely close one of the two
horizontal walls.  This can be compared to some of the
results~\cite{mit-spa2017}.  Do for a variety of distances to
demonstrate how close we can put it to the wall with no need to increase
the resolution}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.35 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{A single body eroding in Stokes flow. Color indicates the shear stress on the body. In this simulation, we use three minimum body-to-wall initial distances $d=h$ (left), $h/2$ (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=0.0001$, and smoothing parameters of $\eps$ and $\sigma $.}
\label{} 
\end{center}
\end{figure}
{\color{red} We first consider a single circular body in a shear flow. 
The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. 
The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$. 
Let the initial radius of the body be $r$, 
the initial length of the body be $L$, $N_\iin$ and 
$N_\out$ be the number of discretization points 
on the body and wall respectively, 
$h=L/N_\iin$ be the resolution mesh size of the body, 
and $d$ be the minimum initial distance from body to wall. 
To investigate the shape of eroding body when it is close to wall, 
we set $r=0.4$, $N_\iin=256$, and $N_\out=1024$ 
with respect to three different $d=h, h/2$, and $ h/10$.

@@

\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense201}
\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed-pressure-drop condition. The color is the vorticity of fluid. The 4 snapshots are evenly spaced in time. In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In the forth frame, bodies 4, 12, and 17 have vanished completely, and body 19 (the one without number on the right) has almost vanished because of eroding.}
\end{center}
\end{figure}
\subsection{20 nearly touching bodies}
{\color{red} 
By using Barycentric quadrature rule, 
we are able to capture the details in the fluid when wall and bodies or body and bodies 
are close to each other. 
The first nearly touching bodies case is 20 bodies in a Hagen-Poiseuille flow. 
The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. 
The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=(1+x_2)(1-x_2)$. 
The number of discretization points $N_\iin$ on the bodies is 256 and the number 
of discretization points $N_\out$ on the outer boundary is 1024.

@@

Besides the channels between two bodies, there is a single channel 
goes across the domain horizontally and
 the flow has been concentrated in this channel. 
In the second frame of Fig.~\ref{fig:Eroding20vort},
 this channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \& 12, and 6 \& 19. 
We can get a better understanding of this channel from 
the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}. 
In the top three frames of  Fig.~\ref{fig:Eroding20tracer},
the flow (or tracer) first comes from three small channels 
between outer boundary \& body 10, bodies 7 \& 14, and bodies 14 \& 18, 
then the three branches become one and go into the main channel between bodies 1 \& 9. 
From the first frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, 
this channel is expanding faster than other channel 
and bodies 4 \& 12 has vanished and body 19 is almost gone in the forth frame. 
The reason of fast expansion of this channel is the high vorticity. 
In the forth frame of Fig.~\ref{fig:Eroding20tracer}, 
we could see the vorticity is relatively high on the side of bodies which form this channel
so the bodies are eroded fast on the side of this channel or have vanished completely.

>>>>

We also do not use any fast summation methods to apply the Barycentric
quadrature rule.  Since this quadrature rule is applied at every GMRES
iteration, it is imperative that we only apply the Barycentric
quadrature at target points where they are required.  As a rule of
thumb, the trapezoid rule due to $\gamma_k$ is accurate if
\begin{align}
  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| > 
    5 \frac{L_k}{N_\iin}.
\end{align}
To avoid having to check if a target point $\xx$ satisifies

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We do some simulations.  The parameters are
\begin{itemize}
  \item time step size
  \item regularization and smoothing parameters
  \item resolution on bodies and solid wall
\end{itemize}
{\color{red} In this section, we present the numerical simulations of bodies eroding in the fluid. The computational domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded off corners and we place bodies only in $[-1,1]\times[-1,1]$. There are $N_\out = 1024$ points on the outer boundary for all the simultions. We impose the fixed pressure drop condition. We use smoothing parameters of $\eps$ and $\sigma$ to control eroding motion on the bodies.  
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A single body close to a wall}
\todo[inline]{Do a single body that is extremely close one of the two
horizontal walls.  This can be compared to some of the
results~\cite{mit-spa2017}.  Do for a variety of distances to
demonstrate how close we can put it to the wall with no need to increase
the resolution}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.35 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{A single body eroding in Stokes flow. Color indicates the shear stress on the body. In this simulation, we use three minimum body-to-wall initial distances $d=h$ (left), $h/2$ (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=0.0001$, and $\eps = 15/256$ and $\sigma=10/256$.}
\label{} 
\end{center}
\end{figure}
{\color{red} We first consider a single circular body in a shear flow. 
The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$. 
Let the initial radius of the body be $r$, 
the initial length of the body be $L$, $N_\iin$ be the number of discretization points 
on the body, 
$h=L/N_\iin$ be the resolution mesh size of the body, 
and $d$ be the minimum initial distance from body to wall. 
To investigate the shape of eroding body when it is close to wall, 
we set $r=0.4$, $N_\iin=256$, and $N_\out=1024$ 
with respect to three different $d=h, h/2$, and $ h/10$.

@@

\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense201}
\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed pressure drop condition. The color is the vorticity of fluid. The 4 snapshots are evenly spaced in time. In this simulation, we use $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In the forth frame, bodies 4, 12, and 17 have vanished completely, and body 19 (the one without number on the right) has almost vanished because of eroding.}
\end{center}
\end{figure}
\subsection{20 nearly touching bodies}
{\color{red} 
By using Barycentric quadrature rule, 
we are able to capture the details in the fluid when wall and bodies or body and bodies 
are close to each other. 
The first nearly touching bodies case is 20 bodies in a Hagen-Poiseuille flow. 
The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. 
The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=(1+x_2)(1-x_2)$. 
The number of discretization points $N_\iin$ on the bodies is 256 and the number 
of discretization points $N_\out$ on the outer boundary is 1024.

@@

Besides the channels between two bodies, there is a single channel 
goes across the domain horizontally and
 the flow has been concentrated in this channel. 
In the second frame of Fig.~\ref{fig:Eroding20vort},
 this channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \& 12, and 6 \& 19. 
We can get a better understanding of this channel from 
the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}. 
In the top three frames of  Fig.~\ref{fig:Eroding20tracer},
the flow (or tracer) first comes from three small channels 
between outer boundary \& body 10, bodies 7 \& 14, and bodies 14 \& 18, 
then the three branches become one and go into the main channel between bodies 1 \& 9. 
From the first frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, 
this channel is expanding faster than other channel 
and bodies 4 \& 12 has vanished and body 19 is almost gone in the forth frame. 
The reason of fast expansion of this channel is the high vorticity. 
In the forth frame of Fig.~\ref{fig:Eroding20vort}, 
we could see the vorticity is relatively high on the side of bodies which form this channel
so the bodies are eroded fast on the side of this channel or have vanished completely.
